---
title: "Why yes, you can use data-processing to find a good PC!"
author: "Florian John"
date: "2023-01-12"
output:
  ioslides_presentation:
    logo: SU_logo_CMYK.png
    incremental: TRUE
    css: slides.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## How ?
```{r,echo=FALSE,warning=FALSE,message=FALSE,include=FALSE,results='hide'}
library(httr)
library(jsonlite)
library(purrr)
library(readxl)
library(robotstxt)
library(rvest)
library(tidyverse)
```

```{r,cache=TRUE,echo=FALSE,include=FALSE,results='hide'}
source_rmd <- function(file, local = FALSE, ...){
  options(knitr.duplicate.label = 'allow')

  tempR <- tempfile(tmpdir = ".", fileext = ".R")
  on.exit(unlink(tempR))
  knitr::purl(file, output=tempR, quiet = TRUE)

  envir <- globalenv()
  source(tempR, local = envir, ...)
}

source_rmd("~/PR_FloJoh/Report/report.Rmd")
```

By for example

* Collecting data
  + Finding csv files about performance of components
  + downloading excel sheets about processor properties
  + Scraping websites of prices and reviews for computers
  
* Analyzing
  + Visualizing what's popular
  + Calculating weighted average review score
  + Comparing pricing vs performance
  
## Collecting data

* Standardize data

  Turn "Intel(R) Core(TM) i5-9600K CPU @ 3.70GHz" 
  
  into "i5-9600K" using `str_extract`:

* scrape and find paths using `html_child` 

  `html_elements() %>% html_children` shows children in the html that you can use to find the wanted element

## Analyzing 

- Join price data and benchmark data

  Using `left_join` find what benchmark score the computers being sold have.

- Group on brand and calculate `weighted.mean` of benchmark data

  We can find what brand has the highest average scores

- Calculate price/performance ratio

  Price/benchmark_score is how much value you get for your money.
  
## Proof it works

```{r,echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}
cpu_flops_data %>% 
  left_join(cpu_data,
            by = "processor") %>% 
  mutate(gflops_per_processor = gflops_per_core*number_of_cores) %>%
  filter(!is.na(base_frequency_ghz)) %>% 
  group_by(cpu_brand) %>% 
  summarise(cpu_brand,
            avg_gflops_per_processor = weighted.mean(gflops_per_processor,w = n_of_computers,na.rm = T)) %>% 
  unique() %>% 
  ggplot(aes(x = cpu_brand,y = avg_gflops_per_processor)) +
  geom_col() +
  labs(
  y = "average GIGAFLOPS",
  title = "Average GIGAFLOPS per processor-brand"
  )
```

## Brands for laptops

```{r}
prisjakt_laptop_table %>% 
  left_join(cpu_benchmark_data[,-3],
            by = "processor") %>% 
  group_by("computer_brand") %>% 
  mutate(
    tot_benchmark_score = sum(cpu_benchmark,na.rm = T),
    price_benchmark_ratio = price/tot_benchmark_score
  ) %>% 
  ggplot(aes(x = computer_brand,y = price_benchmark_ratio)) +
  geom_col()
```

## Brands for desktops

```{r}
desktop_spec_table %>% 
  left_join(cpu_benchmark_data[,-3],
            by = "processor") %>% 
  left_join(gpu_benchmark_data[,-3],
            by = c("graphics_card" = "gpu_name")) %>% 
  group_by("computer_brand") %>% 
  mutate(
    tot_benchmark_score = sum(cpu_benchmark + gpu_benchmark,na.rm = T),
    price_benchmark_ratio = displayed_price_kr/tot_benchmark_score
  ) %>% 
  ggplot(aes(x = computer_brand,y = price_benchmark_ratio)) +
  geom_col()
```

## Thank you
